Combining Linked data and Data Mining Techniques to improve Clustering of Large Scale Media Repositories: A case study with BBC

### 2016-04-27 paper/paper.tex
Using subsections in intro

Approaches used in industry include providing a text-based search, hierarchical
categorisation (and thus navigation thereof) and even more tailored recommended
content based on past behaviour or content enjoyed by friends (or sometimes
simply other consumers who share your preferences), but to build systems
that operate across the full corpus of their content, organisations face
several problems:

@@

\section{Hypothesis}

>>>>

\subsection{Problem}

Approaches to aid discovery of content used in industry include providing a
text-based search, hierarchical
categorisation (and thus navigation thereof) and even more tailored recommended
content based on past behaviour or content enjoyed by friends (or sometimes
simply other consumers who share your preferences), but to build systems
that operate across the full corpus of their content, organisations face
several problems:

@@

\subsection{Hypothesis}
